---
title: "Project 1"
output: html_notebook
---

I used the Hmisc, pastecs, and plotrix libraries.
```{r}
library(Hmisc)
library(pastecs)
library(plotrix)
```

The "stat.desc" function outputs the mean, median, standard deviation, variance, and range.

```{r}
x<-c(57.2, 66.1, 73.1, 72.3, 69.1, 68.9, 54.5, 65.2, 69.3, 67, 71.2, 73)
stat.desc(x)
```

<br>

The "describe" function from Hmisc will tell you how many unique entries you have and how many of each there are.  This is telling you the mode.  
```{r}
describe(x)
```
As you can see from the table each value has a frequency of 1 so there is no mode in this data set.

<br>

The "quantile" function will give you the 0%, 25%, 50%, 75% and 100% quantiles.  You could also use "fivenum" and get the Q1, median, and Q3.
```{r}
quantile(x)
summary(x)
```

<br>

The "IQR" function will give you the interquartile range.
```{r}
cat("IQR = ", IQR(x))
```

<br>

You plot the histogram of the data using the "hist" function.
```{r}
hist(x, main = "Heights of Males", xlab = "Height", col = "blue")
```

<br>

You create a box and whisket plot using the "boxplot" function.
```{r}
boxplot(x, main = "Height of Males", col = "green", ylab = "Height")
```

<br>

Creating the "Pie Chart of Countries"
```{r}
slices<-c(10, 12, 4, 16, 8)
lbls<-c("US", "UK", "Australia", "Germany", "France")
pie(slices, labels = lbls, main = "Pie Chart of Countries")
```

<br>

Creating the "3D Pie Chart of Countries"
```{r}
require(plotrix)
pie3D(slices, labels = lbls, main = "3D Pie Chart of Countries")
```

<br>

Thank you for coming and viewing my document on basic R coding.
Kat Weis
